### 2009-04-07 talk/icooolps2009-dotnet/clibackend.tex
use letters instead of numbers to label the blocks in the picture, to avoid confusion with the "official" numbering described below

Thus, when using the CLI backend, we actually have two JIT compilers at two different levels
layers, each one specialized in different kinds of optimization.
By operating at a higher level, our JIT can potentially do a better job 
in some contexts, as our benchmarks demonstrate (see
Section~\ref{sec:benchmarks}).  On the other hand, the lower-level .NET JIT is
very good at producing machine code, much more than PyPy's own \emph{x86}
backend, for example.  By combining the strengths of both we can get highly
efficient machine code.

@@

\begin{figure}[h]
\begin{center}
\includegraphics[height=5cm]{flexswitch1}
\includegraphics[height=5cm]{flexswitch2}
\caption{An example of a flexswitch evolution: in the picture on the
  right block 7 has been dynamically added.}\label{flexswitch-fig}
\end{center}
\end{figure}

In the pictures of Figure~\ref{flexswitch-fig}, block 5 (highlighted in grey)
corresponds to a flexswitch; initially (picture on the left) 
only block 6, containing the code to restart the JIT compilation,
is connected to the flexswitch; the picture on the right
shows the graph after the first case has been dynamically added to the flexswitch,
by linking block 5 with the freshly created block number 7.

@@

\item Each either primary or secondary method implements a certain
  number of blocks, all belonging to the same flow graph.

\item The parameters of a method correspond to the arguments of what we call the \emph{initial block} of the method.

\end{itemize}

@@

Following an external link whose target is an initial block could also
be easily implemented, by just invoking the corresponding method.
What cannot be easily implemented in CLI is following an external link
whose target is not an initial block; consider, for instance, the
outgoing link from block 7 to block 3 in Figure~\ref{flexswitch-fig}. How is it possible to jump into
the middle of a method?

@@

  public uint execute(int value, InputArgs args) {
    for(int i=0; i<numcases; i++)
      if (values[i] == value)
        return cases[i](0, args);
    return default_blockid;
  }
}
\end{lstlisting}
The mapping from integers values to delegates (pointing to secondary
methods) is just implemented by the two arrays \lstinline{values} and
\lstinline{cases}. Method \lstinline{add_case} extends the mapping
whenever a new case is added to the flexswitch.

>>>>

Thus, when using the CLI backend, we actually have two JIT compilers at two different
layers, each one specialized in different kinds of optimization.
By operating at a higher level, our JIT can potentially do a better job 
in some contexts, as our benchmarks demonstrate (see
Section~\ref{sec:benchmarks}).  On the other hand, the lower-level .NET JIT is
very good at producing machine code, much more than PyPy's own \emph{x86}
backend, for example.  By combining the strengths of both we can get highly
efficient machine code.

@@

\begin{figure}[h]
\begin{center}
\includegraphics[height=5cm]{flexswitch1}
\includegraphics[height=5cm]{flexswitch2}
\caption{An example of a flexswitch evolution: in the picture on the
  right block D has been dynamically added.}\label{flexswitch-fig}
\end{center}
\end{figure}

In the pictures of Figure~\ref{flexswitch-fig}, block B (highlighted in grey)
corresponds to a flexswitch; initially (picture on the left) 
only block C, containing the code to restart the JIT compilation,
is connected to the flexswitch; the picture on the right
shows the graph after the first case has been dynamically added to the flexswitch,
by linking block B with the freshly created block D.

@@

\item Each either primary or secondary method implements a certain
  number of blocks, all belonging to the same flow graph.
\end{itemize}

@@

Following an external link whose target is an initial block could also
be easily implemented, by just invoking the corresponding method.
What cannot be easily implemented in CLI is following an external link
whose target is not an initial block; consider, for instance, the
outgoing link from block D to block A in Figure~\ref{flexswitch-fig}. How is it possible to jump into
the middle of a method?

@@

  public uint execute(int value, InputArgs args) {
    for(int i=0; i<numcases; i++)
      if (values[i] == value)
        return cases[i](0, args);
    return default_blockid;
  }
}
\end{lstlisting}

XXX: add note to explain why we use a for loop instead of an hashtable

XXX: add note to explain who calls execute()

The mapping from integers values to delegates (pointing to secondary
methods) is just implemented by the two arrays \lstinline{values} and
\lstinline{cases}. Method \lstinline{add_case} extends the mapping
whenever a new case is added to the flexswitch.
